Subsegmental language detection in Celtic language text

### 2014-06-27 codeswitch-cltw-2014/codeswitch_camera_ready.tex
update
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@55030 72bbbca6-d526-0410-a7d9-f06f51895060

@@

Restricting the predicted languages to be amongst the two in the dataset was a decision made to identify the language pairs in a better fashion, both by our techniques and by the other tools. Then we used the character trigram probabilities to predict the detected language for each token. Trigrams were chosen after experimenting with 1--5 grams. The heuristics in section~\ref{sec:method} were followed for the text processing and chunking part of the method.

>>>>

As the number of possible languages for each segment is in theory the set of all the world's written languages, we take 
a decision to simplify the task by only looking at texts in the Celtic language and the corresponding majority language spoken
where the Celtic language is spoken. That is, we looked at detecting between Irish and English, Welsh and English 
and Breton and French.

@@

For this system we used the character trigram probabilities to predict the detected language for each token. Trigrams were chosen after experimenting with 1--5 grams. The heuristics in section~\ref{sec:method} were followed for the text processing and chunking part of the method.
